\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2020-07-08 doc/manuscript_acceptedJuly2020.tex
cleaning up

We made forecasts based on two phenomenological statistical models, each representing processes operating at different time scales. One statistical model represents the time-series or ``temporal approach.'' We regressed interannual variation in an ecological response on interannual variation in temperature at just one site. The other statistical model relies on a space-for-time substitution, which we call the ``spatial approach'' for brevity. We regressed the mean temperature on the mean of an ecological state or rate across many sites.  We compared forecasts from both statistical models to the simulated dynamics to determine how well the two approaches performed at different forecast horizons. We also assessed the potential for combining the information available in temporal and spatial patterns by using a weighted average of the forecasts from the temporal and spatial approaches optimized to best match the (simulated) observations. We then studied how the optimal model weights changed over time. We expected the temporal approach to best predict short-term dynamics, the spatial approach to best predict long-term dynamics, while the weighted model would show potential to provide the best forecasts at transitional, intermediate time scales. The three statistical models are described in Supporting Information (Appendix \ref{models}). Computer code for both case studies is available for reviewers online (https://drive.google.com/open?id=1aju04qtQvJmZG1mcpN-6hYBZILBhDfl2) and will be archived at Zenodo upon acceptance. Instructions for running the code are in the README file in the main directory of the zip archive.

@@

\subsubsection*{Data accessibility statement:} The manuscript contains no original data. All computer code is available for reviewers in a zip archive that can be downloaded from Google Drive: https://drive.google.com/open?id=1aju04qtQvJmZG1mcpN-6hYBZILBhDfl2. Upon acceptance of the manuscript, code will be archived at Zenodo.

>>>>

We made forecasts based on two phenomenological statistical models, each representing processes operating at different time scales. One statistical model represents the time-series or ``temporal approach.'' We regressed interannual variation in an ecological response on interannual variation in temperature at just one site. The other statistical model relies on a space-for-time substitution, which we call the ``spatial approach'' for brevity. We regressed the mean temperature on the mean of an ecological state or rate across many sites.  We compared forecasts from both statistical models to the simulated dynamics to determine how well the two approaches performed at different forecast horizons. We also assessed the potential for combining the information available in temporal and spatial patterns by using a weighted average of the forecasts from the temporal and spatial approaches optimized to best match the (simulated) observations. We then studied how the optimal model weights changed over time. We expected the temporal approach to best predict short-term dynamics, the spatial approach to best predict long-term dynamics, while the weighted model would show potential to provide the best forecasts at transitional, intermediate time scales. The three statistical models are described in Supporting Information (Appendix \ref{models}). Computer code for both case studies will be archived at Zenodo upon acceptance. Instructions for running the code are in the README file in the main directory of the zip archive.

@@

\subsubsection*{Data accessibility statement:} The manuscript contains no original data. All computer code will be archived at Zenodo upon acceptance of the paper.
